Supplement for: Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-11-07 manuscripts/supplement.Rmd
update data file names to match figures

@@

@@

write.csv(crash_data, "components/data/figure3.csv")
```

@@

```{r figure_S3, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red."}
gp_assessment_plots$posteriors_plot
```

@@

Training data (Figures 1-6)
----------------------------

Each of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ `r p[1]`, 
$K =$ `r p[2]`, $C =$ `r p[3]`, and  $\sigma_g =$ `r sigma_g` 
for $T=$ `r Tobs` timesteps, starting at initial condition $X_0 = $ `r Xo`. 
The training data can be seen in Figure 1.

Training data for sensitivity analyses
-------------------------------------

A further 96 unique training data sets are generated for the sensitivity analysis, as described in the main text.

Code
----

All code used in producing this analysis can be found in the R package accompanying the paper, available from [http://github.com/cboettig/nonparametric-bayes]. The code for all results shown here is dynamically embedded into the manuscript using `knitr` [@knitr].

<!--
Data
----

While the data can be regenerated using the code provided, for convenience CSV files of the data shown in each graph are also provided, along with appropriate metadata written in the Ecological Metadata Language (EML).

-->

@@

```{r figure_S5, fig.cap="Posteriors from the MCMC estimate of the Ricker model", fig.width=6, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(ricker_posteriors, "components/data/ricker_posteriors.csv")
```

@@

```{r figure_S7, fig.cap="Posterior distributions from the MCMC estimates of the Myers model", fig.width=6, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(myers_posteriors, "components/data/myers_posteriors.csv")
```

@@

```{r figure_S9, fig.cap="Posteriors from the MCMC estimate of the Allen model", fig.width=6, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(allen_posteriors, "components/data/allen_posteriors.csv")
```

@@

Further sensitivity analysis
=============================

@@

```{r figure_S10, fig.height=6, fig.width=10, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histograms shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values of 1 indicate optimal performance. Columns indicate different models, rows different noise levels, and colors indicate the parameter set used. Grouped over stochastic replicates applying the contol policy and stochastic replicates of training data generated from the model indicated, see raw data for details. Randomly chosen parameter values for the models shown in tables below."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=parameters)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/sensitivity_dat.csv") 
```

>>>>

\tableofcontents

@@

<!--
Table of contents? 
-->

# Code #

All code used in producing this analysis has been embedded into the
manuscript sourcefile using the Dynamic Documentation tool, `knitr`
for the R language [@Xie_2013], available at 
[github.com/cboettig/nonparametric-bayes/](https://github.com/cboettig/nonparametric-bayes/)

To help make the mathematical and computational approaches presented
here more accessible, we provide a free and open source (MIT License)
R package that implements the GPDP process as it is presented here.
Users should note that at this time, the R package has been developed
and tested explicitly for this analysis and is not yet intended as a
general purpose tool.  The manuscript source-code described above
illustrates how these functions are used in this analysis. This
package can be installed following the directions above.

## Dependencies & Reproducibility ##

The code provided should run on any common platform (Windows, Mac or Linux)
that has R and the necessary R packages installed (including support for
the jags Gibbs sampler).  The DESCRIPTION file of our R package, `nonparametricbayes`,
lists all the software required to use these methods. Additional software requirements
for the other comparisons shown here, such as the Gibbs sampling for the parametric models,
are listed under the Suggested packages list.

Nonetheless, installing the dependencies needed is not a trivial task, and may 
become more difficult over time as software continues to evolve.  To facilitate
reuse, we also provide a Dockerfile and Docker image that can be used to replicate
and explore the analyses here by providing a copy of the computational environment
we have used, with all software installed. Docker sofware (see [docker.com](http://www.docker.com))
runs on most platforms as well as cloud servers. Use the command:

    docker run -dP cboettig/nonparametric-bayes

to launch an RStudio instance with the necessary software already installed. See the 
Rocker-org project, [github.com/rocker-org](https://github.com/rocker-org) for more 
detailed documentation on using Docker with R.

# Data #

While the data can be regenerated using the code provided, for convenience
CSV files of the data shown in each graph are made available on Dryad.

# Training data #

Each of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ `r p[1]`, 
$K =$ `r p[2]`, $C =$ `r p[3]`, and  $\sigma_g =$ `r sigma_g` for $T=$ `r Tobs`
timesteps, starting at initial condition $X_0 = $ `r Xo`.  The training
data can be seen in Figure 1 and found in the table `figure1.csv`.

## Training data for sensitivity analyses ##

A further 96 unique randomly generated training data sets are generated
for the sensitivity analysis, as described in the main text.  The code
provided replicates the generation of these sets.

# Model performance outside the predicted range

@@

write.csv(crash_data, "components/data/figureS1.csv")
```

# MCMC analyses #

This section provides figures and tables showing the traces from each of the MCMC runs used to estimate the parameters of the models presented, along with the resulting posterior distributions for each parameter.  Priors usually appear completely falt when shown against the posteriors, but are summarized by tables the parameters of their corresponding distributions for each case.

@@

```{r figure_S3, fig.cap="Posterior distributions from the MCMC estimate of the GP model. Prior curves shown in red."}
gp_assessment_plots$posteriors_plot
write.csv(gp_dat,"components/data/figureS2-3.csv")
```

@@

@@

```{r figure_S5, fig.cap="Posteriors from the MCMC estimate of the Ricker model", fig.width=6, fig.height=4}
ggplot(ricker_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(ricker_posteriors, "components/data/figureS4-5.csv")
```

@@

```{r figure_S7, fig.cap="Posterior distributions from the MCMC estimates of the Myers model", fig.width=6, fig.height=6}
ggplot(myers_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(myers_posteriors, "components/data/figureS6-7.csv")
```

@@

```{r figure_S9, fig.cap="Posteriors from the MCMC estimate of the Allen model", fig.width=6, fig.height=6}
ggplot(allen_posteriors, aes(value)) + 
  stat_density(geom="path", position="identity") +
  facet_wrap(~ variable, scale="free", ncol=2)
write.csv(allen_posteriors, "components/data/figureS8-9.csv")
```

@@

# Further sensitivity analysis #

@@

```{r figure_S10, fig.height=6, fig.width=10, dependson=c("sensitivity-calc", "export-data"), fig.cap="Sensitivity Analysis.  Histograms shows the ratio of the realized net present value derived when managing under the GPDP over the optimal value given the true model and true parameters. Values of 1 indicate optimal performance. Columns indicate different models, rows different noise levels, and colors indicate the parameter set used. Grouped over stochastic replicates applying the contol policy and stochastic replicates of training data generated from the model indicated, see raw data for details. Randomly chosen parameter values for the models shown in tables below."}
ggplot(sensitivity_dat) + 
  geom_histogram(aes(value, fill=parameters)) + 
  xlim(0,1.0) + 
  theme_bw() + 
  xlab("value as fraction of the optimal") + 
  facet_grid(noise~model)
write.csv(sensitivity_dat, "components/data/figureS10.csv") 
```
